%% Template file for all Software/Hardware modules

% Replace "Name of Module" with the name of this module
\subsection{Satellite}

\subsubsection{Description}

This module describes the architecture of how the back end will manage features related to managing Satellites. 

The Satellite Management back end is in control of maintaining the information in the database pertaining to Satellites. 
The back end will also generate the framework for the web pages. 
It will pass the basic form of the Satellite Management page to the front end to be filled in with additional formatting. 

\subsubsection{Program Flow}

The back end Satellite Management module will be activated by a request from the front end Satellite Management. 
This module will complete the request by adding information to the \ac{SQL} database or querying said database for specific data. 

\subsubsection{Data Flow}

The Data Flow will behave in much the same manner as the Program Flow. 
The back end Satellite Management module will receive data from the Satellite Management front end via the \ac{REST} \ac{API}. 
This includes data that needs to be changed in the database, and requests for data. 
This module will then modify or query the database as needed, 
returning the requested data or a confirmation of modification to the front end through the \ac{REST} \ac{API}. 

\subsubsection{Sub-modules}
Communication with the Satellites:\\
This modules serves as an interface and a form listener. 
It will receive \ac{POST}ed commands for dispatch to the ZigBee network via a serial-port connected ZigBee. 
It will also receive the incoming data from the ZigBee network and store it in the Database. 
The data will consist of the current and voltage readings from each Satellite on the network. 

\subsubsection{Objects}

The Satellite module consists of the following objects:

\begin{table}[H]
  \centering
  \caption{satellite/models.py}
  \label{code:satellite/models}
  \input{codes/satellite/models.py}
\end{table}