%% Template file for all Software/Hardware modules

% Replace "Name of Module" with the name of this module
\subsection{Devices}

\subsubsection{Description}

This module describes the architecture of how the frontend will create pages that allow the user to manage devices in the system. 

It will receive a basic framework for the web pages in HTML from the back end module and use Javascript to render the rest of the page. 
The pages will be created with a mix of HTML and CSS from the back end and heavy Javascript from this module. 
The Device Management front end includes the Device Management page, Add Devices page, and the Confirm Disable Device dialog. 


\subsubsection{Program Flow}

The user will be presented with the option to add, edit, or disable a Device. 
Adding a Device allows the user to name the new Device and associate it with a specific Satellite. 
Editing a Device allows the user to change the Satellite associated with the Device. 
The user will not have the option to edit the name of the Device once it has been created in order to maintain consistant data. 
Disabling a Device will remove it from all graphs and tables and data will no longer be collected on the Device.
Devices cannot be deleted in order to maintain past data.

\subsubsection{Data Flow}

The data will be sent to the Device Management back end module through the REST API. 
The back end returns either a confirmation of action or the requested data to the front end via the API. 
This module receives the basic format for the web pages from the back end Device module. 
It then fills in the additional and page-specific content. 

%\subsubsection{Potential Problems}

% A list of potentional programs along with suggestions
%  on ways to work around them.
%  Elaborate on why the problem exists
