
\chapter{Use Cases}

The following tasks are broken down into several simple steps. 
Although they do not account for things like "find the button to click", 
it is clear when a user is expected to click a button.\\

The "Actors" section describes the things that will play a role in this scenario. 
These can include:
\begin{itemize}
	\item Users
	\item The Display
	\item The Satellite
\end{itemize}

\paragraph{Users}
The Users are any customer who has permission to access the Display or add and remove Satellites.

\paragraph{The Display}
In terms of the User, the Display is the web page that the User accesses in their web browser.

\paragraph{The Satellite}
The Satellites are the outlett nodes that devices are plugged into. These are the gadgets that will measure the power usage of each device. 


The "Assumptions" section describes assumptions that are made for this scenario. 
These include things such as "User is logged in", or "Several Satellites are connected".\\

The "Procedure" describes the procedure that is taken to by the user to accomplish the goal. \\

The "Expected Outcome" is the ultimate goal. 
It is what the user expects to happen after they execute the procedure. 
These can be visual outputs, stored data, or even changes to the way the system behaves.\\

Listed below are all following Use Cases in order.
\begin{itemize}
	\item Logging In
	\item Logging Out
	\item View Monthly Power Consumption
	\item View Largest Power Consumer
	\item View Power Consumption Over Time
	\item Adjust Power Cost
	\item Add User
	\item Delete User
	\item Add Device
	\item Rename Device
	\item Disable Device
	\item Re-enable Device
	\item Remap Device
	\item Adding a Satellite
	\item Removing a Satellite
\end{itemize}